Life in the canopy: Phylogenetic filtering and morphological canalization in epiphytic ferns

### 2019-07-28 ms/manuscript.Rmd
Update MS

Surprisingly, SLA was only slightly lower in epiphytes relative to terrestrial species (\fig \@ref(fig:cwm-div), \tab \@ref(tab:pics). Specific leaf area is an important part of the leaf economic spectrum, which posits that leaf traits including SLA, N and C content, and leaf life span vary along well-defined axes such that plants generally fall into one of two categories: fast-growing species with high SLA, low nutrient content, and short life spans vs. slow-growing species with low SLA, high nutrient content, and long life spans [@Wright2004a]. We hypothesized that epiphytes would have lower SLA, given their more extreme growing conditions. Indeed, the species with the lowest SLA values were epiphytes (\eg, *Davallia anderssonii* Mett. ex Kuhn, \SI{`r smallest_sla_1`} {\square\meter\per\kilo\gram}; *Ctenopterella blechnoides* (Grev.) Parris, \SI{`r smallest_sla_2`} {\square\meter\per\kilo\gram}), but this relationship was not significant across the dataset (\fig \@ref(fig:cwm-div), \tab \@ref(tab:pics)). The tradeoffs posited in the leaf economics spectrum have been most thoroughly documented in global studies including the widest possible range of taxa and environments, and do not always hold up in local studies [@Petter2016]. For example, @Zhu2016 did not find a significant relationship between SLA and leaf life span in a survey of 16 ferns across a disturbance (light) gradient in China. It is possible that other small-scale effects (\eg, microclimate) obscure this pattern in local studies such as ours and that of @Zhu2016. This is supported by the strong, parallel relationship in CWM values of SLA with elevation in both epiphytes and terrestrial species (\fig \@ref(fig:cwm-div)).

>>>>

Surprisingly, SLA was only slightly lower in epiphytes relative to terrestrial species (\fig \@ref(fig:cwm-div), \tab \@ref(tab:pics). Specific leaf area is an important part of the leaf economic spectrum, which posits that leaf traits including SLA, N and C content, and leaf life span vary along well-defined axes such that plants generally fall into one of two categories: fast-growing species with high SLA, low nutrient content, and short life spans vs. slow-growing species with low SLA, high nutrient content, and long life spans [@Wright2004a]. We hypothesized that epiphytes would have lower SLA, given their more extreme growing conditions. Indeed, the species with the lowest SLA values were epiphytes (\eg, *Davallia anderssonii* Mett. ex Kuhn, \SI{`r smallest_sla_1`} {\square\meter\per\kilo\gram}; *Ctenopterella blechnoides* (Grev.) Parris, \SI{`r smallest_sla_2`} {\square\meter\per\kilo\gram}), but this relationship was not significant across the dataset (\fig \@ref(fig:cwm-div), \tab \@ref(tab:pics)). The tradeoffs posited in the leaf economics spectrum have been most thoroughly documented in global studies including the widest possible range of taxa and environments, and do not always hold up in local studies [@Petter2016; @Messier2017]. For example, @Zhu2016 did not find a significant relationship between SLA and leaf life span in a survey of 16 ferns across a disturbance (light) gradient in China. It is possible that other small-scale effects (\eg, microclimate) obscure this pattern in local studies such as ours and that of @Zhu2016. This is supported by the strong, parallel relationship in CWM values of SLA with elevation in both epiphytes and terrestrial species (\fig \@ref(fig:cwm-div)).
